Scikit-learn: machine learning without learning the machinery

### 2014-05-21 article.tex
Finish the unsupervised learning part

\paragraph{Model evaluation and parameter selection}
%
The data used to train a model can be used to measure the prediction
error, as it would be enable to distinguish noise from signal, and thus
overly optimistic. The correct way is to leave out \emph{test} data,
untouched during training. Often a \emph{cross-validation} scheme is
used, where the data is repeatedly split into \emph{train} and
\emph{test} subsets. Scikit-learn provides a complete framework for
cross-validation. Specific iterators are used to describe the subsets and
several functions and objects accept as arguments these iterators to
perform cross-validation internally. For instance the {\tt
cross\_val\_score} function measures the prediction score of an
estimator.

CV objects: GridSearchCV and RandomSearchCV, as well as FooBarCV objects.

\paragraph{Unsupervised models: learning to transform}
%
Unsupervised learning: a variety of usage pattern.

Many things can be seen as Transformers

Introduce the pipeline

>>>>

\paragraph{Model evaluation and parameter selection}
%
The data used to train a model can be used to measure the prediction
error, as it would be enable to distinguish noise from signal, and thus
overly optimistic. The correct way is to leave out \emph{test} data,
untouched during training. Often a \emph{cross-validation} scheme is
used, where the data is repeatedly split into \emph{train} and
\emph{test} subsets. Scikit-learn provides a complete framework for
cross-validation. Specific iterators are used to describe the subsets and
several functions and objects accept as arguments these iterators to
perform cross-validation internally. For instance the {\tt
cross\_val\_score} function measures the prediction score of an
estimator. Cross-validation can also be used to tuned the meta-parameters
of an estimator, such as the sparsity of a sparse model. For this,
specific estimators, \emph{meta-estimators}, such as the {\tt
GridSearchCV}, take another estimator at construction time, and use
cross-validation internally to set its parameter. When used together with
{\tt cross\_val\_score}, they perform \emph{nested} cross-validation,
\emph{i.e.}~the meta-parameters are set independently of the test data?

\paragraph{Unsupervised models: learning to transform}
%
Unsupervised learning covers all learning applications in which there is
no clearly identified variable to predict. For instance, in a clustering
application, the task is to group together observations that are similar.
Dimension reduction tries to find simplified representations that capture
well the properties of the data. Novelty detection finds in a new dataset
observations that differ from the data in the train set. As the uses of
unsupervised learning are very diverse, it is not possible to have an API
as uniform as for supervised learning. While some unsupervised
estimators can be used to predict a characteristic of new data, such as
in novelty detection, many are useful to transform data, as in dimension
random. Scikit-learn estimators can have a {\tt transform} method, used
for this purpose. A {\tt Pipeline} estimator can then chain estimators to
form a new estimator that applies transformations before calling the {\tt
fit} or {\tt predict} method of the last object.
